\section{Status}
\label{ch:Status}

\begin{frame}{Status}
From last time, we discussed a few items, namely:

\begin{itemize}
	\item Bad matching with Data Derived Bunch z-profiles
		\begin{itemize}
			\item Could this be because bunch models are not overlapping at z = 0?
			\item Are Beam Profiles appropriately centered?
		\end{itemize}
	\item Can we improve performance with a simple lookup, as opposed to TGraph::Eval?
	\item Profiles might introduce artifacts resembling crossing angles/different
		values for $\beta^{*}$.
\end{itemize}

\end{frame}

\begin{frame}{Progress}
	\begin{itemize}
    \item Density lookup has been implemented, code now runs nice and fast
		\item Direct comparison between beam profiles from WCM data + simple model
			are ready - maybe this provides some insight?
		\item Studied bunch profiles - although all profiles line up relative to
			each-other, the maximum of the bunch profile was not centered.
		\item New method:
			\begin{itemize}
				\item Find global maxima in WCM profile
				\item Build profile starting from the center, moving left and right
				\item Stop when we hit the edge of the data set
				\item The rest of the profile is set to "0"
				\item Possible option (to account for beam gas, peripheral bunch
					distributions in Z):
					\begin{itemize}
						\item Sample background of WCM profile, and fill the peripheral bunch
							distribution with random fluctuations based on sampled region
					\end{itemize}
			\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Issues}
There are still remaining issues with the simulation, the z-profile in the ZDC
z-vertex distribution is still not matching nicely when we use the WCM data
directly. Some thoughts:
	\begin{itemize}
    \item Have we selected an appropriate interaction time?
    \item Is $\beta^{*}$ correction applied correctly to the width?
    \item Could binning be effecting the final profile?
    \item Should the old model even be used as a bench-mark?
	\end{itemize}
\end{frame}
